The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
landcover clarifications

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at <!-- TODO: double check --> 30m resolution. We reclassified the
landcover types into three categories: foraging habitat, open habitat, and
forest habitat. Foraging habitat consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.
<!-- using the raster package for R? -->

>>>>

### Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at <!-- TODO: double check --> 10m resolution. We reclassified the
landcover types into three categories: foraging habitat, open habitat, and
forest habitat. Foraging habitat <!-- or just lichen like figs?--> consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.
<!-- using the raster package for R? -->
